---
title: "ManyAnalysts"
author: "Brendan Barrett and Tracy Montgomery"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load data
library(rethinking)
d_demo <- read.csv("Data/demographics.csv")
d_discp <- read.csv("Data/displacements.csv")
d_groom <- read.csv("Data/grooming.csv")
d_ot <- read.csv("Data/observation_times.csv")
str(d_demo)
str(d_discp)
str(d_groom)
str(d_ot)
sort(unique(d_demo$ID)) == sort(unique(d_groom$Sender)) # true all represented
sort(unique(d_groom$Sender)) == sort(unique(d_groom$Receiver)) # true all represented
sort(unique(d_groom$Receiver)) ==  sort(unique(d_demo$ID)) # true all represented
str(d_groom)
d_groom$r_index <- as.integer(as.factor(d_groom$Receiver))
d_groom$s_index <- as.integer(as.factor(d_groom$Sender))
dens(d_groom$Duration_seconds)
range(d_groom$Duration_seconds)

```


```{r g}
## Load data
library(janitor)
d_demo <- clean_names(read.csv("Data/demographics.csv"))
d_disp <- clean_names(read.csv("Data/displacements.csv"))
d_groom <- clean_names(read.csv("Data/grooming.csv"))
d_ot <- clean_names(read.csv("Data/observation_times.csv"))
str(d_demo)
str(d_discp)
str(d_groom)
str(d_ot)
```


```{r}
## Load data
d_demo <- read.csv("Data/demographics.csv")
d_discp <- read.csv("Data/displacements.csv")
d_groom <- read.csv("Data/grooming.csv")
d_ot <- read.csv("Data/observation_times.csv")
str(d_demo)
str(d_discp)
str(d_groom)
str(d_ot)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
